---
title: plotRCS
author: Author by Rongrui Huo
output: github_document
---

```{r, message = FALSE, tidy = FALSE, echo = F}
showMessage <- FALSE
showWarning <- TRUE
knitr::set_alias(w = "fig.width", h = "fig.height", res = "results")
knitr::opts_chunk$set(comment = "##", error= TRUE, warning = showWarning, message = showMessage,
               tidy = FALSE, cache = FALSE, echo = TRUE,
               fig.width = 5, fig.height = 4.5,
               fig.path = "README-files/README_")

## R configuration
options(width = 116, scipen = 5)
```

# Description

Simple drawing of restricted cubic spline (RCS) curves through '**ggplot2**' package from a linear regression model, a logistic regression model or a Cox proportional hazards regression model.

# Package NEWS

* Changes in version 0.1.4
* Support for a linear regression model

# Installation

The stable release version can be installed directly from CRAN using:
```{r, eval=FALSE}
install.packages("plotRCS")
```

Alternatively, the development version can be installed using the **devtools** R-Package:
```{r, eval=FALSE}
# Install devtools (if you do not have it already)
install.packages("devtools")

devtools::install_github("kunhuo/plotRCS")
```

or the **remotes** R-Package:
```{r, eval=FALSE}
install.packages("remotes")

remotes::install_github("kunhuo/plotRCS")
```

# Bug Reports and Feature Requests

If you encounter any bugs or have any specific feature requests, please file an [Issue](https://github.com/KunHuo/plotRCS/issues).

# Examples

## RCS curves for a linear regression model

```{r}
library(plotRCS)

# View data
head(cancer)

# RCS curves for a liear regression model
rcsplot(data = cancer,
        outcome = "size",
        exposure = "age",
        covariates = c("sex", "race", "metastasis"))
```

## RCS curves for a logistic regression model

```{r}
# RCS curves for a logistic regression model
rcsplot(data = cancer,
        outcome = "status",
        exposure = "age",
        covariates = c("sex", "race", "size", "metastasis"))
```


## RCS curves for a Cox regression model

```{r}
rcsplot(data = cancer,
        outcome = "status",
        time = "time",
        exposure = "age",
        covariates = c("sex", "race", "size", "metastasis"))
```

