---
title: "Introduction to plotRCS"
output: github_document
---

```{r, message = FALSE, tidy = FALSE, echo = F}
showMessage <- FALSE
showWarning <- TRUE
knitr::set_alias(w = "fig.width", h = "fig.height", res = "results")
knitr::opts_chunk$set(comment = "##", error= TRUE, warning = showWarning, message = showMessage,
               tidy = FALSE, cache = FALSE, echo = TRUE,
               fig.width = 7, fig.height = 7,
               fig.path = "README-files/README_")

## R configuration
options(width = 116, scipen = 5)
```

# Installation

This version of plotRCS package for R is developmetal, and may not be available from the CRAN. You can install it using one of the following way.

**Direct installation from github**

You first need to install the devtools package to do the following. You can choose from the latest stable version and the latest development version.

```{r, eval=FALSE}
# Install devtools (if you do not have it already)
install.packages("devtools")
# Install directly from github (develop branch)
devtools::install_github("kunhuo/plotRCS")
```

**Direct installation from CRAN**

```{r, eval=FALSE}
install.packages("plotRCS")
```

